---
title: "Untitled"
author: "Justin"
date: "2023-08-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```










# Redo the analysis

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
```



```{r}
# dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
# uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")


```

## Balance between treated and controls
```{r}

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  filter(complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
  add_p()

```



##  Trends over time

```{r}
## Plot
p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
  group_by(`BHCMIS ID`, Year) %>%
  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count))


plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
  geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none") 

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000)


p.desc <- ggarrange(plot1, plot0) 

annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))


```



## Overall Effects on Key Variables
```{r}

df.core <- dfc %>% 
  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100, 
         
         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,Qcomp, Altman, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman) 
  
df.core2 <- df.core


did.core <- c(0, 0, 0, 0)

for (j in 10:12){
  
  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.core <- rbind(did.core, outcomes$coeftable)
}


did.core <- did.core[-1,]
rownames(did.core) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Altman) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Altman) %>% 
  mutate(value = round(value, 2)) %>% 
  filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z")) %>% 
   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = NiceName) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))



p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") , 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE, nrow = 1 ) 
p0

```


## Broken down by components
```{r}

df.core <- dfc %>% 
  mutate( MCD = Total * Pct.MCD / 100,
         None = Total * Pct.None / 100,
         MCR = Total * Pct.MCR / 100,
         COM = Total * Pct.COM / 100,
         
         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         MCD:COM, 
         crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman) 
  



did.core <- c(0, 0, 0, 0)

for (j in 10:23){
  
  df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )
  
  did.core <- rbind(did.core, outcomes$coeftable)
  
  
}


did.core <- did.core[-1,]
rownames(did.core) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(MCD:NetWorth) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = MCD:NetWorth) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

```



## Panel Complexity and Intensity of Care
```{r}

df.select.stint <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100, 
         
         pap.denom = pap.denom / Total * 100, 
         crc.denom = crc.denom / Total * 100, 
         adultbmi.denom = adultbmi.denom / Total * 100, 
         childbmi.denom = childbmi.denom / Total * 100, 
         htn.denom = htn.total / Total * 100, 
         dm.denom = dm.total / Total * 100) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
         PatientsPerStaff = ngla_prog_serv_revenue / Total, #Total / Staff, 
         ProgramCostPerPatient = log(ngla_expense / Total)) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Complexity, Intensity, PatientsPerStaff, ProgramCostPerPatient, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

  


did.select.stint <- c(0, 0, 0, 0)

for (j in 10:12){
  
  df.temp <- df.select.stint[,c(1:9, j, 12:ncol(df.select.stint))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.select.stint <- rbind(did.select.stint, outcomes$coeftable)
}


did.select.stint <- did.select.stint[-1,]
rownames(did.select.stint) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)

p1 <- df.select.stint %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Complexity:PatientsPerStaff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Complexity:PatientsPerStaff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.select.stint) %>% 
        
  #       , group =   gsub(x = df.select.stint %>% 
  # select(Complexity:Intensity) %>% 
  # colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
  # arrange(desc(group)) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

p1



p2 <- ggarrange(
  event_study(data = df.select.stint, 
  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") , 
event_study(data = df.select.stint, 
  yname = "Intensity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity"), common.legend = TRUE ) 
p2




```


## Early vs Late competitors (pre-post ACA?)

```{r}


df.ppACA <- df.core2 %>% 
  mutate(EarlyLate = ifelse(Att == 0, 0, 
                     ifelse(Att %in% c(2012:2014), 1,# 2))) 
                     ifelse(Att %in% c(2015:2017), 2, 3))))
  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>% 


did.ppACA <- c(0, 0, 0, 0)
for (i in 1:3){
for (j in 10:12){
  
  df.temp <- df.ppACA[,c(1:9, j, 13:ncol(df.ppACA))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(EarlyLate %in% c(0, i)) , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.ppACA <- rbind(did.ppACA, outcomes$coeftable)
}
}

did.ppACA <- did.ppACA[-1,]
rownames(did.ppACA) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)



data.frame(Subset = sort(rep(c("2012-2014","2015-2017","2018-2021"), 3)),
      Outcome = rep(c("Total","Quality","Financial"), 3),
      Estimate = as.numeric(did.ppACA[,1]), 
      SD = as.numeric(did.ppACA[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #liquids based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",liquid=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by timeperiod of competitive shocks")

```



## Effects stratified by profitability

```{r}


#splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.333, 0.667), na.rm = TRUE)



splits <- c(mean(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, na.rm = TRUE))

#splits <- c(-0.03, 0.1)

df.profit <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100, 
         
         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
  ungroup()#, #pap.rate:dm.total, Liquidity:Altman) 
  
df.profit <- df.profit %>% 
  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets) %>% 
  mutate(pc = ngla_net_gain_loss / ngla_expense) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
  

splits1 <- c(min(df.profit$pc, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))


did.profit <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){
  
  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(pc > splits1[g] & pc <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )
  
  did.profit <- rbind(did.profit, outcomes$coeftable)
  
}}


did.profit <- did.profit[-1,]
rownames(did.profit) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)




plot.profit <- data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  #mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ylab("Stratified by baseline profitability (% of expenses)") + 
  ggtitle("DID Estimates by Baseline Profitiability")

plot.profit
```





## Effects startified by clinic size
```{r}

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(dfc[dfc$year.rel == -1,]$Total, c(0.5), na.rm = TRUE)

splits <- mean.nas(dfc[dfc$year.rel == -1,]$Total)

df.size <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100, 
         
         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
  ungroup()#, #pap.rate:dm.total, Liquidity:Altman) 
  
df.size <- df.size %>% 
  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, Total) %>% 
  mutate(Size = Total) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
  

splits1 <- c(min(df.size$Size, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.size$Size, na.rm = TRUE))



did.size <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){
  
  df.temp <- df.size[,c(1:9, j, 13:ncol(df.size))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(Size > splits1[g] & Size <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )
  
  did.size <- rbind(did.size, outcomes$coeftable)
  
}}


did.size <- did.size[-1,]
rownames(did.size) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)




data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.size[,1]), 
      SD = as.numeric(did.size[,2])) %>% 
  #mutate(Subset.f = as.factor(Subset)) %>% 
  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ylab("Stratified by baseline clinic population size") + 
  ggtitle("DID Estimates by Baseline Size")

```




## Effects startified by liquidity
```{r}

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(dfc[dfc$year.rel == -1,]$quick_ratio, c(0.5), na.rm = TRUE)

splits <- mean.nas(dfc[dfc$year.rel == -1,]$quick_ratio)

df.liquid <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100, 
         
         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
  ungroup()#, #pap.rate:dm.total, Liquidity:Altman) 
  
df.liquid <- df.liquid %>% 
  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, quick_ratio) %>% 
  mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
  

splits1 <- c(min(df.liquid$liquid, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.liquid$liquid, na.rm = TRUE))



did.liquid <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){
  
  df.temp <- df.liquid[,c(1:9, j, 13:ncol(df.liquid))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(liquid > splits1[g] & liquid <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )
  
  did.liquid <- rbind(did.liquid, outcomes$coeftable)
  
}}


did.liquid <- did.liquid[-1,]
rownames(did.liquid) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)




data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.liquid[,1]), 
      SD = as.numeric(did.liquid[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #liquids based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",liquid=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Liquidity")

```






## Stratified effects in linearized fashion
```{r}

did2s(
      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )

did2s(
      data = df.size  %>% mutate(Size = Size / 1000 ), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * Size) + I(Tx * Size^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )

did2s(
      data = df.liquid %>% filter(!is.na(liquid)) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * liquid) + I(Tx * liquid^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )
```




## OTher splits

Splits
- Total at 10000 and at 25000
- ngla_net_gain_loss/ngla_revenue at 0.03 (Profitable grow and give up financial footing, unprofitable improve quality)
- Months of cash at 2

Significant Variables
- Qcomp
- Total
- Sites
- Staff
- Quick-ratio

```{r}

summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.67), na.rm = TRUE)


dfc.new <- dfc %>% 
        select(ID, Year, Tx, Att, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities, 
               Qcomp:Altman)
      

df.temp  


did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )


event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
              inner_join(dfc %>% filter(Year == 2010 )# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) 


```






## Changes in geographic distribution of resources by Distance to competitive zip

```{r}

## Treatment vs control, only in zip code of interest
df.z <- left_join(dfc #%>% filter(`Grant Number` != "H80CS00225")
                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
                    filter(Year %in% c(2010:2021)) %>% 
              select(`BHCMIS ID`, Zip) %>%
              unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
  filter(!is.na(GrantNumber)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25) 

df.z <- df.z %>%
  left_join(df.z %>%
            filter(Tx.z == 1) %>%
            group_by(ID, Zip) %>%
            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)


## Whole zip as one measure

df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
  select(Zip, Att.z, Year) %>% 
  unique() %>% 
  left_join(uds.zip, by = c("Zip" = "ZipCode", "Year" = "ReportingYear")) %>% 
  left_join(dfc %>% 
            select(`BHCMIS ID`, Year, Qcomp), by = c("BHCMISID" = "BHCMIS ID", "Year")) %>% 
  group_by(Zip, Year, Att.z) %>% 
  summarise(
    Total.z = sum(NumberofPatients, na.rm = TRUE), 
    Quality.z = sum(NumberofPatients * Qcomp, na.rm = TRUE) / Total.z) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),


df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)



```

## DIstance Rival Traveled
```{r}

## Distance of Competitor to New Site
df.z.dist <- df.z.full %>% 
  filter(Att.z == Year) %>% 
  select(Zip:Total.z) %>% 
  left_join(uds.sites.full %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  left_join(df.z %>% filter(Tx == 1) %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  filter(`BHCMIS ID.x` != `BHCMIS ID.y`) 

## Read in Centroid Data
zip.centroids <- read.csv("/Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)

for (g in 1:nrow(df.z.dist)){
#g <- 1
 temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
          zip.centroids %>% filter(ZipCode %in% unique(uds.sites.full[uds.sites.full$`BHCMIS ID` == df.z.dist[g,]$`BHCMIS ID.x` & uds.sites.full$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
   unique()
  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
}

#df.z.dist[19,]$DistToClosestSite <- 0
df.z.dist <- df.z.dist %>% 
  filter(!is.infinite(DistToClosestSite))

df.z.dist <- df.z.dist %>% 
  inner_join(df.z.dist %>% group_by(`BHCMIS ID.y`) %>% summarise(Att.z = min(Att.z)), by = c("BHCMIS ID.y", "Att.z")) %>% 
  unique()

mean(df.z.dist$DistToClosestSite)
quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

# mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
# mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
# 
# quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
# quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))


zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)


## Original Figure
df.z.dist.plot <- df.z.dist %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
         l.density = log(TotalPop / Area.SQmiles)) %>% 
  unique()



df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")

summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))



# Updated Figure
df.z.dist.plot <- df.z.dist.plot %>% 
  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.Origin = TotalPop / Area.SQmiles)


df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
  ylab("Distance from Competative to closest Rival Site (km)") +
  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")


p <- df.z.dist.plot %>% 
  filter(DistToClosestSite < 200) %>% 
  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
  scale_colour_gradientn(colours = c("green","lightblue","purple"),
                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
  xlab("Log Population Density of Nearest Service Area Zip Code") + 
  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
p


summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))

df.z.dist.plot %>% 
  arrange(desc(DistToClosestSite))
```




## Primary effects by distance rival travelled
```{r}
set.seed(123)
df.dist <- df.core2 %>% 
  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite, Density.NewZip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite / df.z.dist.plot$Density.NewZip), replace = TRUE), 
         Dist.random = ifelse(Att > 0, DistToClosestSite / Density.NewZip, Dist.random))




#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)


splits1 <- c(min(df.dist$Dist.random, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.dist$Dist.random, na.rm = TRUE))



did.dist <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){
  
  df.temp <- df.dist[,c(1:9, j, 13:ncol(df.dist))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(Dist.random > splits1[g] & Dist.random <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )
  
  did.dist <- rbind(did.dist, outcomes$coeftable)
  
}}


did.dist <- did.dist[-1,]
rownames(did.dist) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)




data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.dist[,1]), 
      SD = as.numeric(did.dist[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Distance Traveled")
```



## Rival selecting where to put new site, takes 30+ minutes to work

```{r}

## Build the first part of the dataset

df.spill <- df.z %>% 
  left_join(df.z.dist %>% 
  select(`BHCMIS ID.y`, Zip) %>% 
    unique() %>% 
    rename(ZipOfComp = Zip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  #filter(!is.na(ZipOfComp)) %>% 
  #mutate(ZipOfComp = ifelse(`BHCMIS ID` == "H80CS00765", 95991, ZipOfComp)) %>% 
  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
  left_join(zip.centroids, by = c("ZipOfComp" = "ZipCode")) %>% 
  mutate(Dist = sqrt((X.x - X.y) ^ 2 + (Y.x - Y.y) ^ 2) * 111.139) %>% 
  mutate(Dist.f = ifelse(is.na(Dist), "-1",
                  ifelse(Dist == 0, 0, 
                  ifelse(Dist > 0 & Dist < 20, 1, 
                  ifelse(Dist >= 20 & Dist < 50, 2, 
                  ifelse(Dist >= 50 & Dist < 100, 3, 4)))))) %>% 
  #filter(is.na(Dist.f) | Dist.f == 2) %>% 
  left_join(uds.sites.full %>% 
              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year, Zip) %>% 
              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMIS ID","Year", "Zip")) %>% 
  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar))

dist.vecs <- df.spill[!is.na(df.spill$Dist),]$Dist

df.spill %>% 
  group_by(Dist.f) %>% 
  summarise(n())



## Find neighbors based on some circle around FQHC zip

mm <- dist(zip.centroids[,2:3])
mm <- as.matrix(mm) * 111.139

mm.2 <- mm[zip.centroids$ZipCode %in% unique(df.spill$Zip),]

mm.2 <- as.matrix((mm.2 < 50) + 0 )
rowSums(mm.2)



mm.3 <- c(CenterZip = 0, Year = 0, Competing.Sites = 0)
for (g in 1:dim(mm.2)[1]){
  mm.3 <- rbind(mm.3, cbind(CenterZip = zip.centroids[rownames(mm.2)[g],]$ZipCode, zip.centroids[names(mm.2[g,][which(as.vector(mm.2[g,] == 1))]),]) %>% 
  left_join(uds.sites.full %>% filter(Year %in% c(2010:2021)) %>% group_by(Year, Zip) %>% summarise(Sites.Total = n()), by = c("ZipCode" = "Zip")) %>% 
  left_join(df.spill %>% select(`BHCMIS ID`, Year, Zip, Sites), by = c("ZipCode" = "Zip", "Year")) %>% 
  mutate(Sites.Total = ifelse(is.na(Sites.Total), 0, Sites.Total), 
         Sites = ifelse(is.na(Sites), 0, Sites), 
         Competing.Sites = Sites.Total - Sites) %>% 
  filter(CenterZip != ZipCode) %>% 
  group_by(CenterZip, Year) %>% 
  summarise(Competing.Sites = sum(Competing.Sites)) %>% 
    as.matrix())
}

mm.3 <- mm.3[-1,]

#mm.100 <- mm.3 %>% data.frame() 
#mm.60 <- mm.3 %>% data.frame() 
#mm.50 <- mm.3 %>% data.frame() 
#mm.20 <- mm.3 %>% data.frame() 
#mm.10 <- mm.3 %>% data.frame() 

#mm.3 <- mm.50 


```



```{r}

df.spill2 <- df.spill %>% 
  left_join(mm.3 %>% data.frame() %>% mutate(Year = as.numeric(Year)), by = c("Zip" = "CenterZip","Year")) %>% 
  mutate(Competing.Sites = as.numeric(ifelse(is.na(Competing.Sites), 0, Competing.Sites)), 
         D = ifelse(Competing.Sites > 0, 1, 0))

#length(unique(df.spill2[is.na(df.spill2$Dist),]$Zip))  #1893 or 1893 * 5

set.seed(234)  #232
df.spill2 <- df.spill2 %>% 
  group_by(Zip) %>% 
  mutate(Dist = ifelse(is.na(Dist), sample(dist.vecs, 1, replace = T), Dist), 
                                  Att.viz = ifelse(Att == 0, rep(sample(c(2012:2021), 1, replace = T), each = 1), Att)) %>% 
  mutate(Dist.rounded = as.factor(ceiling(Dist / 10))) 


df.spill2 <- df.spill2 %>% 
  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) %>%
  #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) # %>% filter(ZipFilter == 2)



p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")



suppressWarnings(print(p.spill))


```





## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}

zipsize2 <- zctas(starts_with = unique(c(df.spill2$Zip)), year = 2010)


df.spill3 <- df.spill2 %>% 
  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles))
  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
  #        Unemployed = Unemployed / Unemp_denom, 
  #        Elderly = Age65andOver / TotalPop, 
  #        Black = Black / TotalPop, 
  #        Hispanic = Hispanic / TotalPop)

 i <- 10
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]


for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}
  

  

did.access.figures <- df.spill3 %>% 
    mutate(Post = ifelse(Att.viz >= Year, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total.Hours, Perminance:Private) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total.Hours:Private) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total","Uninsured","Medicaid","Medicare","Private")) %>% 
  select(Outcome, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted) %>% 
  cbind(TEs %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`)) %>% 
  cbind(TEs_Dist %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`))



did.access.figures <- did.access.figures[c(5:9, 1, 3, 2, 4),]
rownames(did.access.figures) <- NULL

 did.access.figures %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patients" = 5, "Access" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))

 
summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0& df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
 
 
```



## Effect of Competition on Rival
```{r}

    
df.rival <- dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
  bind_rows(dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(!is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
    left_join(df.comp%>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100) %>% 
    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.Homeless)
  
  

did.rival <- c(0, 0, 0, 0)

for (j in 10:18){
  
  df.temp <- df.rival[,c(1:9, j, 19:ncol(df.rival))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.rival <- rbind(did.rival, outcomes$coeftable)
}


did.rival <- did.rival[-1,]
rownames(did.rival) <- NULL

mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)

df.rival %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Pct.COM) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Pct.COM) %>% 
  mutate(value = round(value, 2)) %>% 
  filter(name %in% c("Total", "MCD","None","MCR","COM","Pct.MCD", "Pct.None","Pct.MCR","Pct.COM")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.rival, NiceName = c("Total","Medicaid, total", "Uninsured, total","Medicare, total","Private, total","Medicaid, %", "Uninsured, %","Medicare, %","Private, %")) %>% 
   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = NiceName) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Total Patients by Insurnace" = 5, "Payor Mix, Proportion" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

event_study(data = df.competitor, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
  
  
```


